It’s COMPAS-licated Can We Find Fairness in the COMPAS Risk Assessment Algorithm?

### 2022-03-07 Paper_Draft1/Draft1.Rmd

---
title: Full title of the paper (Capitalized)
author:
  -author:
  - name: Amrita Acharya
    affil: 1, 2
  - name: Dianne Caravela
    affil: 1, 3
  - name: Eunice Kim
    affil: 1, 4
  - name: Emma Kornberg
    affil: 1, 5
  - name: Elisabeth Nesmith
    affil: 1, 6
affiliation:
  - num: 1
    address: |
      Statistical and Data Sciences
      Smith College
      Northampton, MA 01063
  - num: 2
    email: aacharya@smith.edu
  - num: 3
    email: dcaravela@smith.edu
  - num: 4
    email: ekim89@smith.edu
  - num: 5
    email: ekornberg@smith.edu
  - num: 6
    email: enesmith@smith.edu
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: water
type: article
status: submit
bibliography: mybibfile.bib
csl: ../resources/chicago-author-date.csl
appendix: appendix.tex

>>>>

---
title: It’s COMPAS-licated Can We Find Fairness in the COMPAS Risk Assessment Algorithm?
author:
  - name: Amrita Acharya
    affil: 1, 2
  - name: Dianne Caravela
    affil: 1, 3
  - name: Eunice Kim
    affil: 1, 4
  - name: Emma Kornberg
    affil: 1, 5
  - name: Elisabeth Nesmith
    affil: 1, 6
affiliation:
  - num: 1
    address: |
      Statistical and Data Sciences
      Smith College
      Northampton, MA 01063
  - num: 2
    email: aacharya@smith.edu
  - num: 3
    email: dcaravela@smith.edu
  - num: 4
    email: ekim89@smith.edu
  - num: 5
    email: ekornberg@smith.edu
  - num: 6
    email: enesmith@smith.edu

correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: water
type: article
status: submit
bibliography: mybibfile.bib
csl: ../resources/chicago-author-date.csl
appendix: appendix.tex
